\documentclass[11pt,a4paper, sans]{moderncv}

\moderncvstyle{classic}  % 'casual', 'classic', 'oldstyle' or 'banking'
\moderncvcolor{blue}
\nopagenumbers{}

\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% personal data
\firstname{Antoine}
\familyname{Albertelli}
%\title{EPFL Student}
\address{Ch. de l'Auverney 9}{1814 La Tour-de-Peilz}
\mobile{079~384~38~62}
\phone{021~944~45~44}
\email{antoine@antoinealb.net}
\homepage{antoinealb.net}
%\photo[64pt][0.4pt]{neko}

\begin{document}
\makecvtitle

\section{Education}
\cventry{2016--current}{MSc in Microengineering}{EPFL}{Lausanne}{}{}
\cventry{2010--2014}{BSc in Microengineering}{EPFL}{Lausanne}{}{}

\section{Employment history}

\cventry{2015--Current}{Founder, Software Engineer}{WISE Robotics}{Lausanne}{}{
    Co-founded an engineering consultancy.
    We develop custom solutions in the fields of robotics and embedded systems (e.g. Internet of Things appliances).
    My main role is system design and software engineering, both on low power systems (micro-controllers) in C/C++ and destkop/servers applications in Python.
}
\cventry{2015}{Civil service}{CRYOS Lab, EPFL}{Lausanne}{}{
    Wrote a data analysis pipeline for manipulating large weather datasets using Python for processing and SQLite for intermediate results storage.
    Assisted with the setup of experimental weather measurement stations in various areas.
}
\cventry{2014--2015}{Civil service}{Lemaitre Lab, EPFL}{Lausanne}{}{
    Helped with research in social psychology, leading to the publication of a book and of an article (to be published).
}
\cventry{2013--2014}{Warehouse work}{La Poste}{Eclépens}{}{}
\cventry{2011--2014}{Student assistant}{EPFL}{Lausanne}{}{Student assistant for various programming courses.}
\cventry{2012}{Warehouse work}{Adecco}{Vevey}{}{}

\section{Activities}
\cventry{2008--Current}{Robotics contest}{}{}{}{
    I took part in the Eurobot contest with my team and we were qualified to take part in the world finals in 2009, 2013 and 2014.
    We also won the Swiss contest and the technical award in 2014.\\
    Some of the technical challenges I worked on were the port of existing code to a new RTOS running on an FPGA, as well as the integration of an embedded TCP/IP stack.
    We recently switched to a distributed architecture (around 30 nodes in one robot) and I am currently working on making the new setup more stable as it caused us issues.
}

\cventry{2007--Current}{Roleplaying games}{}{}{}{
    I regularly play roleplaying games, both as a player and a game master.
    I helped organize introduction sessions geared toward people unfamiliar with the hobby.
}

\section{Languages}
\cvlanguage{French}{Native speaker}{}
\cvlanguage{English}{Fluent}{}
\cvlanguage{German}{Intermediate}{}

\section{Computer tools}
\cvitem{Proficient}{C/C++, Git, Mercurial, Linux, Python, Office, Matlab, Docker, SaltStack}
\cvitem{Known}{SolidWorks, KiCAD, OpenGL, AVR Assembly}

\section{Work Interests}
\cvitem{Engineering}{Control systems, Manufacturing technologies, Process engineering}
\cvitem{Software}{High reliability software, Test Driven Development, Continuous Delivery, Embedded software}
\end{document}

